---
title: "Project_2"
=======:
author: "Greg Ricalde, Amelia Kelly & Matt Wilchek"
date: "April 8, 2017"
output:
  ioslides_presentation:
    css: bulma.css
    smaller: yes
    transition: slower
    widescreen: yes
runtime: shiny
subtitle: An Exploratory Data Analysis
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# Install necessary packages and include packages.
library(ggplot2) # for graphing
library(lattice) # for graphing
library(car) # for graphing
library(memisc) # for function case
library(HistData) # library containing data
library(grid) # for graphing
library(rsconnect) # for publishing to Shiny apps
library(RCurl)
x <- getURL("https://raw.githubusercontent.com/mwilchek/GWU_Project.AnalyzingClimateChange/master/GlobalTemperatures.csv")
y <- read.csv(text = x)
head(y)

```

### 1. Question

## 2. Current Climate Change Research

## 3. Data Gathering, Impute/Prep Methods
  
## 4. Exploratory Data Analysis

## 5. Maps

## 6. Climate Change Model

## 7. Predictions

## 8. Examples

## Shiny Presentation

This R Markdown presentation is made interactive using Shiny. The viewers of the presentation can change the assumptions underlying what's presented and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Interactive Plot

```{r eruptions}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

## Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## R Output

```{r cars}
summary(cars)
```


